Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-09-22 R0V0.tex
Add header
Change header
Restructure the paper into design of decentralized controllers and decentralized design of decentralized controllers.
Move proofs from the Proofs section

@@

\section{Results}\label{sec:Results}

@@

The detailed proof of Theorem \ref{thm:main result} is provided in Section \ref{sec:Proof of the Results}.

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel. The next result provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$. Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

@@

The detailed proof of Corollary \ref{cor:distributed computation} is provided in Section \ref{sec:Proof of the Results}.

@@

\section{Proof of the Results}\label{sec:Proof of the Results}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 																			   %
% Git Branch: Manchester20160725											   %
% 																			   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Design of Decentralized Controllers}\label{sec:Design of Decentralized Controllers}

@@

Although Theorem \ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori} the computation of the MI \eqref{eq:MI formulation}  cannot be done in parallel. The next section provides sufficient conditions to solve each component \eqref{eq:MI formulation} independently, and according to the structure defined by the set $\Xi$. Before present it, the following concept of block-diagonally dominant matrix is recalled from \cite{ZhangLiChen2006}.

\section{Distributed Design of Decentralized Controllers}

@@

@@
